pirouette: the error BEAST2 makes in inferring a phylogeny

### 2019-02-26 article.tex
Simplify scripts

  \textbf{1. }
    BEAST2 is a popular Bayesian phylogenetics software tool,
    that takes an alignment and inference model to create a
    posterior of jointly-estimated phylogenies and model parameter estimates.
    When a new macro-evolutionary diversification model is developed,
    a good first step is to measure the error BEAST2 makes on a known
    phylogeny derived from a new diversification mechanism, 
    with its current set of inference models. \\
  \textbf{2. }
    Here, we present a free, libre and open-source R package, \verb;pirouette;
    that assesses the inference error BEAST2 makes based on a known/true 
    phylogeny. \\
  \textbf{3. }
    We describe \verb;pirouette;'s usage and the biological scientific
    question it can answer, including full examples. \\
  \textbf{4. }
    As \verb;pirouette; is designed to be of high quality and extendable, 
    we conclude by describing the further development of the package. \\
\end{abstract}

@@

The development of new powerful inference tools, 
such as BEAST [\cite{drummond2007beast}] or MrBayes [\cite{huelsenbeck2001mrbayes}], 
allowed to build phylogenetic trees 
from genetic material extracted from extant organisms.
This has constituted an important step forward 
in our understanding on how species 
evolve.
Such tools have been increasingly exploited to hypothesize and test what are the main drivers and modes for diversification processes.

>>>>

  \textbf{1. }
    BEAST2 is a popular Bayesian phylogenetics software tool,
    that takes an alignment and inference model to create a
    posterior of jointly-estimated phylogenies and model parameter estimates.
    When a new macro-evolutionary diversification model is developed,
    a good first step is to measure the error BEAST2 makes on a known
    phylogeny derived from a new diversification mechanism, 
    with its current set of inference models. \\
  \textbf{2. }
    Here, we present a free, libre and open-source R package, \verb;pirouette;
    that assesses the inference error BEAST2 makes based on a known/true 
    phylogeny. \\
  \textbf{3. }
    We describe \verb;pirouette;'s usage and the biological scientific
    question it can answer, including full examples. \\
  \textbf{4. }
    Last, we'll discuss the results obtained by the examples. \\
\end{abstract}

@@

The development of new powerful inference tools, 
such as BEAST [\cite{drummond2007beast}], MrBayes [\cite{huelsenbeck2001mrbayes}]
or RevBayes [\cite{hohna2016revbayes}], 
allowed to build phylogenetic trees 
from genetic material extracted from extant organisms.
This has constituted an important step forward 
in our understanding on how species 
evolve.
Such tools have been increasingly exploited to hypothesize and test what are the main drivers and modes for diversification processes.
